---
output: github_document
---

# FinalProjectGroup6

Before running our linear regression model, it is necessary to initialize the two input variables:\
  `x`: matrix with number of rows representing the number of response (explanatory) variable\
  `y`: vector representing the predictions\
  
We are using the `bank.csv` dataset as an example.
  
```{r}
library(FinalProjectGroup6)
df <- read.csv2("bank.csv", header = TRUE)
df$job <- as.numeric(as.factor(df$job))
df$marital <- as.numeric(as.factor(df$marital))
df$education <- as.numeric(as.factor(df$education))
df$default <- as.numeric(as.factor(df$default))
df$housing <- as.numeric(as.factor(df$housing))
df$loan <- as.numeric(as.factor(df$loan))
df$contact <- as.numeric(as.factor(df$contact))
df$month <- as.numeric(as.factor(df$month))
df$poutcome <- as.numeric(as.factor(df$poutcome))
df$y <- as.numeric(as.factor(df$y))


x <- df[, -which(names(df) == "y")]
y <- df$y
```

The next step is to run the model by calling the `our_lm` function.

```{r}
model <- our_lm(y, x, alpha = 0.05)
```

The individual results returned from the model can be obtained by running a command similar to below.

```{r}
# F-statistic
model$f_stat
```

Plots for the residuals can also be generated.

```{r}
# residuals vs fitted-values
res_plot(model$res, model$preds)

# qq-plot
qq_plot(model$res)

# histogram
histogram(model$res)
```
