---
title: "Linear Regression - Group 6"
output: rmarkdown::html_vignette
css: mystyles.css
vignette: >
  %\VignetteIndexEntry{Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---


[Package Repository: Final_Project_Group6](https://github.com/AU-R-Programming/Final_Project_Group6)

The Package name is "FinalProjectGroup6".


Before running our linear regression model, it is necessary to initialize the two input variables:\
  `x`: matrix with number of rows representing the number of predictors (explanatory) variables\
  `y`: vector representing the response variable\
  
We are using the `bank.csv` dataset as an example.
  
```{r}
library(FinalProjectGroup6)
df <- read.csv2("bank.csv", header = TRUE)
df$job <- as.numeric(as.factor(df$job))
df$marital <- as.numeric(as.factor(df$marital))
df$education <- as.numeric(as.factor(df$education))
df$default <- as.numeric(as.factor(df$default))
df$housing <- as.numeric(as.factor(df$housing))
df$loan <- as.numeric(as.factor(df$loan))
df$contact <- as.numeric(as.factor(df$contact))
df$month <- as.numeric(as.factor(df$month))
df$poutcome <- as.numeric(as.factor(df$poutcome))
df$y <- as.numeric(as.factor(df$y))

# defining the input variables
x <- df[, -which(names(df) == "y")]
x <- x[c("age", "balance", "duration")] #selected 3 predictors
y <- df$y 
```

The next step is to run the model by calling the `our_lm` function. We further, compare our results to that of the built-in `lm` function. We can see that the results are very similar.

```{r}
model <- our_lm(y, x, alpha = 0.05)
model2 <- lm(y ~ x$age + x$balance + df$duration)
model$beta
model2$coefficients
```
To obtain the desired outputs by subsetting the model to the desired output. For example, we can obtain the p-value and F-statistic of the model by running the following command:

```{r}
#p-value
model$p_value

# F-statistic
model$f_stat
```

Plots for the residuals can also be generated.

```{r, fig.show='hold'}
# residuals vs fitted-values
res_plot(model$res, model$preds)

# qq-plot
qq_plot(model$res)

# histogram
histogram(model$res)
```
